---
title: "SS3 Diagnostic Plots"
resource_files:
- Rscripts/helper_functions_SS3.R
runtime: shiny
output: flexdashboard::flex_dashboard
---

```{r global, include=FALSE}

options(shiny.sanitize.errors = FALSE)

dirMain <-getwd()
dirRScripts <- paste(dirMain,"/Rscripts/",sep='')

# parameter and run/seed info
dirWS <- "https://goo.gl/mo1Tz7"
# dirWS    <- paste(dirMain, "/data/", sep="")
# dirData    <- paste(dirMain, "/data/", sep="")
dirData <- "http://mdst-macroes.ird.fr:8080/thredds/dodsC/BlueBridge/IOTC/"
#######################################################

########### SOURCE LIBRARIES AND FUNCTIONS ############
library(shiny)
require(rCharts)
library(plyr)
library(reshape2)
library(ggplot2)
library(ncdf4)
library(flexdashboard)
library(plotly)

run_parameters <- read.csv(dirWS)
# run_parameters <- read.csv(paste(dirWS, "run_spec_ss3.csv", sep=""))
r_seed <- 1
#######################################################

```


```{r, include=FALSE}
source(paste(dirRScripts,'helper_functions_SS3.R',sep=''))
## extract CPUE data from .nc files - Obs_cpue, Exp_cpue, Dev_cpue, and calculate standardised deviations
  CPUE_plot <- reactive({read_CPUE_data(paste(input$Model),input$Run, dir_save=paste(dirData,sep=''))})
## extract Lenbase data from .nc files - Obs_len, Exp_len
  LEN_plot <- reactive({read_LEN_data(paste(input$Model),input$Run, dir_save=paste(dirData,sep=''))})
## extract Recruitment Deviation data from .nc files - RecDev_val, RecDev_lci, RecDev_uci
  RecDev_plot <- reactive({read_RecDev_data(paste(input$Model),input$Run,dir_save=paste(dirData,sep=''))})
## extract Recruitment_0 data from .nc files - re0
  R0_plot <- reactive({read_R0_data(paste(input$Model),input$Run,dir_save=paste(dirData,sep=''))})
## extract SSB data from .nc files - re0
  SSB_plot <- reactive({read_SSB_data(paste(input$Model),input$Run,dir_save=paste(dirData,sep=''))})
## extract Total biomass data from .nc files - Biomass_all_ts
 Bio_plot <- reactive({read_Bio_data(paste(input$Model),input$Run,dir_save=paste(dirData,sep=''))})
## extract F/Fmsy data from .nc files - FFmsy
  FFMSY_plot <- reactive({read_ffmsy_data(paste(input$Model),input$Run,dir_save=paste(dirData,sep=''))})
## extract size selectivity data from .nc files - sizeselex
  Ssel_plot <- reactive({read_Ssel_data(paste(input$Model),input$Run,dir_save=paste(dirData,sep=''))})
## extract age selectivity data from .nc files - ageselex
  Asel_plot <- reactive({read_Asel_data(paste(input$Model),input$Run,dir_save=paste(dirData,sep=''))})
```

  
Select input {.sidebar}
===================================== 
  **Please select your model/run(s) HERE. **

```{r}
selectInput(inputId='Model',
               label='Select from the species models currently available',
               choices=as.character(unique(run_parameters$Model)),
               selected='SWO',
               multiple = FALSE)
output$selectUI <- renderUI({
  selectInput("Run", 
              label="Choose the run(s) to plot", 
              choices =  as.character(run_parameters$Run[run_parameters$Model==input$Model]), 
              # selected=as.character(run_parameters$Run[1]),
              selected=as.character(run_parameters$Run[run_parameters$Model==input$Model][1]),
              multiple=TRUE)
})
htmlOutput("selectUI")
```


CPUE
===================================== 
Compare observations (black) against the predictions (colored) of selected SS3 model/run(s) for CPUE. 

Column {.tabset}
-----------------------------------------------------------------------

### CPUE Fit

```{r}
renderPlotly({
    CPUE2plot <- CPUE_plot()
    ############# CPUE FIT: OBSERVED V PREDICTED ###########
    p <- ggplot(na.exclude(CPUE2plot), aes(x=Year, y=Obs))
    p <- p+geom_point(size=0.7,col='black')+geom_line(col='black')+geom_line(aes(y=Exp, colour=Model_run))+
      facet_wrap(~Fleet,ncol=2,)#+scales='free_y'+ggtitle("CPUE fit: Observed v Predicted")#as.numeric(as.character(input$Run)))
    ggplotly(p)
    ########################################################
  })

```

### Standardized CPUE residuals
```{r}
renderPlotly({
    CPUE2plot <- CPUE_plot()
    ################# CPUE STANDARDIZED RESIDUALS ###################
    p <- ggplot(na.exclude(CPUE2plot), aes(x=Year, y=stDev, colour=Model_run))
    p <-  p+geom_point()+geom_line()+
      facet_wrap(~Fleet,ncol=2)+geom_abline(intercept = -2,slope=0, col="blue",linetype=2)+
      geom_abline(intercept = 2,slope=0, col="blue",linetype=2)+
      geom_abline(intercept = 0,slope=0, col="blue",linetype=2)#+ggtitle("Standardized CPUE residuals")
    ggplotly(p)
    #################################################################
  })
```

Size Frequency
===================================== 
Size frequency by fleet, including mean aggregated length frequency (cm), mean length distribution (cm), and mean weight distribution (kg).

Column {.tabset}
-----------------------------------------------------------------------

### Aggregated Length Frequency
```{r}
renderPlotly({
    LEN2plot <- LEN_plot()
    ###################### AGGREGATE LENGTH FREQUENCY ########################
    forLen <- ddply(na.exclude(LEN2plot), .(Fleet,Bin,Model_run), function(x) data.frame(Obs=sum(x$Obs), Exp=sum(x$Exp)))
    
    p <- ggplot(forLen, aes(x=Bin, y=Obs))
    p <- p+geom_bar(stat="identity")+facet_wrap(~Fleet, ncol=3, scales="free")+
      geom_line(aes(y=Exp,colour=Model_run))+ylab('Observations')+xlab('Length bin (cm)')#+ 
      # ggtitle("Aggregated length frequency")
    ggplotly(p)
    ##########################################################################
})
```

### Mean Length Distribution
```{r}
renderPlotly({
    LEN2plot<-LEN_plot()
    ##################### MEAN LENGTH DISTRIBUTION ###########################
    forLen2 <- ddply(na.exclude(LEN2plot), .(Fleet,Year,Model_run), function(x) data.frame(Obs=weighted.mean(x=x$Bin, w=x$Obs), 
                                                                           Exp=weighted.mean(x=x$Bin, w=x$Exp) ))
    p <- ggplot(forLen2, aes(x=Year, y=Obs))
    p <- p+geom_point()+geom_line(col="black")+geom_line(aes(y=Exp,colour=Model_run))+
      facet_wrap(~Fleet,scales = 'free', ncol=3)+ylab('Length (cm)')
    ggplotly(p)
    ##########################################################################
})

```

### Mean Weight Distribution
```{r}
renderPlotly({
    LEN2plot<-LEN_plot()
    ##################### MEAN LENGTH DISTRIBUTION ###########################
    forLenWeight <- ddply(na.exclude(LEN2plot), .(Fleet,Year,Model_run), function(x) data.frame(Obs=3.815e-006*(weighted.mean(x=x$Bin, w=x$Obs))^3.188,                                                     Exp= 3.815e-006*(weighted.mean(x=x$Bin, w=x$Exp))^3.188 ))
    p <- ggplot(forLenWeight, aes(x=Year, y=Obs))
    p <- p+geom_point()+geom_line(col="black")+geom_line(aes(y=Exp,colour=Model_run))+
      facet_wrap(~Fleet, scales='free',ncol=3)+ylab('Weight (kg)')
    ggplotly(p)
    ##########################################################################
  })
```

Biomass
===================================== 
Biomass figures, including total biomass (1000 t), depletion (%), and spawning stock biomass (SSB; 1000 t): by area and summed over areas.
  

Column {.tabset}
-----------------------------------------------------------------------


### Total Biomass by Area
```{r}
renderPlotly({
  Bioplot<-Bio_plot()
  ########################## TOTAL BIOMASS BY AREA ########################
  end_current_period=max(Bioplot$Year[Bioplot$Era=='TIME' & is.na(Bioplot$bio)==FALSE])
  # req(is.null(which(colnames(Bioplot)=='Area')))
   if(length(intersect(colnames(Bioplot),'Area'))>0){ ## check that the model is multi-area
  forBA <- ddply(na.exclude(Bioplot), .(Area,Year,Model_run),
                 function(x) data.frame(bio=sum(x$bio[x$Era=="TIME"|x$Era=="FORE"],na.rm=T)/1000))
    forBA0<-forBA[which(forBA$bio>0),]
  
  p <- ggplot(forBA0, aes(x=Year, y=bio,colour=Model_run))
  p <- p+geom_line(stat="identity")+facet_wrap(~Area, ncol=2)+ylab('Total Biomass (x1000 t)')+
     geom_vline(xintercept = end_current_period,col="blue",linetype=2)
  ggplotly(p)  
  
  }else{  ## condition if single-area model, will plot total biomass
    
    forBAtot <- ddply(na.exclude(Bioplot), .(Year,Model_run),
                      function(x) data.frame(bio=sum(x$bio[x$Era=="TIME"|x$Era=="FORE"],na.rm=T)/1000))
    forBAtot0<-forBAtot[which(forBAtot$bio>0),]

    p <- ggplot(forBAtot0, aes(x=Year, y=bio,colour=Model_run))
    p <- p+geom_line(stat="identity")+ylab('Total Biomass (x1000 t)')+ylim(range(forBAtot$bio))+
      geom_vline(xintercept = end_current_period,col="blue",linetype=2)+ggtitle('single-area model')
    ggplotly(p)
  }
  #########################################################################
})
```

### Total Biomass
```{r}
renderPlotly({
  Bioplot<-Bio_plot()
   end_current_period=max(Bioplot$Year[Bioplot$Era=='TIME' & is.na(Bioplot$bio)==FALSE])
  ########################## TOTAL BIOMASS (SUMMED OVER AREA) ########################
  forBAtot <- ddply(na.exclude(Bioplot), .(Year,Model_run),
                 function(x) data.frame(bio=sum(x$bio[x$Era=="TIME"|x$Era=="FORE"],na.rm=T)/1000))
  forBAtot0<-forBAtot[which(forBAtot$bio>0),]
  
  p <- ggplot(forBAtot0, aes(x=Year, y=bio,colour=Model_run))
  p <- p+geom_line(stat="identity")+ylab('Total Biomass (x1000 t)')+ylim(range(forBAtot$bio))+
     geom_vline(xintercept = end_current_period,col="blue",linetype=2)
  ggplotly(p)
  #########################################################################
})
```

### Depletion by Area
```{r}
renderPlotly({
  Bioplot<-Bio_plot()
  end_current_period=max(Bioplot$Year[Bioplot$Era=='TIME' & is.na(Bioplot$bio)==FALSE])
  
  if(length(intersect(colnames(Bioplot),'Area'))>0){ 
    forBA <- ddply(na.exclude(Bioplot), .(Area,Year,Model_run),
                 function(x) data.frame(bio=sum(x$bio[x$Era=="TIME"|x$Era=="FORE"],na.rm=T)/1000))
  forBA0<-forBA[which(forBA$bio>0),]
  
  ######################## % DEPLETION BY AREA ############################
  p <- ggplot(forBA0, aes(x=Year, y=bio/bio[1]*100,colour=Model_run))
  p <- p+geom_line(stat="identity")+facet_wrap(~Area, ncol=2)+ylab('Depletion (%)')+
 geom_hline(yintercept=40,col='dark grey')+
     geom_vline(xintercept = end_current_period,col="blue",linetype=2)
  ggplotly(p)
  #########################################################################
  }else{
    forBAtot <- ddply(na.exclude(Bioplot), .(Year,Model_run), 
                 function(x) data.frame(bio=sum(x$bio[x$Era=="TIME"|x$Era=="FORE"],na.rm=T)/1000))
    forBAtot0<-forBAtot[which(forBAtot$bio>0),]
  
  p <- ggplot(forBAtot0, aes(x=Year, y=bio/bio[1]*100,colour=Model_run))
  p <- p+geom_line(stat="identity")+ylab('Depletion (%)')+ylim(0,max(forBAtot0$bio/forBAtot0$bio[1]*100))+
     geom_hline(yintercept=40,col='dark grey')+
     geom_vline(xintercept = end_current_period,col="blue",linetype=2)+ggtitle('single-area model')
  ggplotly(p)
  }
   })
```

### Depletion
```{r}
renderPlotly({
  Bioplot<-Bio_plot()
  end_current_period=max(Bioplot$Year[Bioplot$Era=='TIME' & is.na(Bioplot$bio)==FALSE])
  
  ##################### % DEPLETION (SUMMED OVER AREAS) ###################
  forBAtot <- ddply(na.exclude(Bioplot), .(Year,Model_run), 
                 function(x) data.frame(bio=sum(x$bio[x$Era=="TIME"|x$Era=="FORE"],na.rm=T)/1000))
     forBAtot0<-forBAtot[which(forBAtot$bio>0),]
  
  p <- ggplot(forBAtot0, aes(x=Year, y=bio/bio[1]*100,colour=Model_run))
  p <- p+geom_line(stat="identity")+ylab('Depletion (%)')+ylim(0,max(forBAtot0$bio/forBAtot0$bio[1]*100))+
     geom_hline(yintercept=40,col='dark grey')+
     geom_vline(xintercept = end_current_period,col="blue",linetype=2)
  ggplotly(p)
  #########################################################################
   })
```


### SSB by Area
```{r}
renderPlotly({
  SSBplot<-SSB_plot()
   if(length(intersect(colnames(SSBplot),'Area'))>0){ 
  #################### SPAWNING STOCK BIOMASS BY AREA #####################
  forSSB <- ddply(na.exclude(SSBplot), .(Area,Year,Model_run),
                 function(x) data.frame(spbio=sum(x$spbio[x$Era=="TIME"]))) ### <--AEN: GLOBAL ATTRIBUTES FOR CHARACTERS!!!
  zeros=which(forSSB$spbio>0)
  forSSB<-forSSB[zeros,]

  p <- ggplot(forSSB, aes(x=Year, y=spbio,colour=Model_run))
  p <- p+geom_line(stat="identity")+facet_wrap(~Area, ncol=2)+ylab('Spawning Biomass (x1000 t)')
  ggplotly(p)
  ##########################################################################
   }else{
     forSSBtot <- ddply(na.exclude(SSBplot), .(Year,Model_run),
                 function(x) data.frame(spbio=sum(x$spbio[x$Era=="TIME"]))) 
  forSSBtot0<-forSSBtot[which(forSSBtot$spbio>0),]
  
  p <- ggplot(forSSBtot0, aes(x=Year, y=spbio,colour=Model_run))
  p <- p+geom_line(stat="identity")+ylab('Spawning Biomass (x1000 t)')+ggtitle('single-area model')
  ggplotly(p)
   }
})
```

### SSB
```{r}
renderPlotly({
  SSBplot<-SSB_plot()
  ####################### SPAWNING STOCK BIOMASS ########################### 
  forSSBtot <- ddply(na.exclude(SSBplot), .(Year,Model_run),
                 function(x) data.frame(spbio=sum(x$spbio[x$Era=="TIME"]))) 
  forSSBtot0<-forSSBtot[which(forSSBtot$spbio>0),]
  
  p <- ggplot(forSSBtot0, aes(x=Year, y=spbio,colour=Model_run))
  p <- p+geom_line(stat="identity")+ylab('Spawning Biomass (x1000 t)')
  ggplotly(p)
  # ##########################################################################
})
```

Fishing Mortality
===================================== 
Compare observations against the predictions of selected SS3 model(s) for fishing mortality. 
  

Column {.tabset}
-----------------------------------------------------------------------

### F/F_msy
```{r}
renderPlotly({
  FFMSYplot<-FFMSY_plot()
  ####################### FFMSY (SUMMED OVER AREAS) ###########################
   p <- ggplot(FFMSYplot, aes(x=Year, y=FFmsy,colour=Model_run))
  p <- p+geom_line(stat="identity")+ylab('F/Fmsy')
  ggplotly(p)
  ##########################################################################
})
```


Recruitment
===================================== 
Compare observations against the predictions of selected SS3 model(s) for recruitment deviation, recruitment (millions) by area, and summed over area  (millions). 
  
Column {.tabset}
-----------------------------------------------------------------------

### Recruitment Deviation
```{r}
renderPlotly({
  # RecDevplot<-RecDev_plot()
  xx <- rnorm(1000,0,0.2)
  x1 <- quantile(xx, 0.025)
  x2 <- quantile(xx, 0.975)

  # ####################### RECRUITMENT DEVIATION ###########################
  # plot(RecDevplot$Year, RecDevplot$value, type="l", lwd=2, xlab="Year", ylab="Rec dev", ylim=c(min(x1,RecDevplot$value,na.rm=T),max(x2,RecDevplot$value,na.rm=TRUE)), xaxt ="n")
  # 
  # # polygon(c(RecDevplot$Year, rev(RecDevplot$Year)), c(RecDevplot$uci, rev(RecDevplot$lci)), border=NA, col="light grey" )
  # 
  # lines(RecDevplot$Year, RecDevplot$value, lwd=2)
  # axis(1, at=seq(min(RecDevplot$Year),max(RecDevplot$Year),5))
  # lines(range(RecDevplot$Year), rep(0,2), lty=3)
  # lines(range(RecDevplot$Year), rep(x1,2), lty=4, col="blue")
  # lines(range(RecDevplot$Year), rep(x2,2), lty=4, col="blue")
  # ##########################################################################
  # 
  # 
  
   RecDevplot<-RecDev_plot()
  ####################### RECRUITMENT (SUMMED OVER AREAS) ###########################
  forRecDev <- ddply(na.exclude(RecDevplot), .(Year,Model_run),
                 function(x) data.frame(value=sum(x$value))) 
  # zeros=which(forRecDev$rec0>0)
  # forRecDev<-forRecDev[zeros,]

  p <- ggplot(forRecDev, aes(x=Year, y=value,colour=Model_run))
  p <- p+geom_line(stat="identity")+ylab('Recruitment deviation')+
     geom_hline(yintercept=x1,col='blue')+
     geom_hline(yintercept=x2,col='blue')+
     geom_hline(yintercept=0,col='blue')
  ggplotly(p)
  ##########################################################################

  
})
```

### Recruitment by Area
```{r}
renderPlotly({
  R0plot<-R0_plot()
  if(length(intersect(colnames(R0plot),'Area'))>0){ 
  ####################### RECRUITMENT BY AREA ###########################
  forR0 <- ddply(na.exclude(R0plot), .(Area,Year,Model_run),
                 function(x) data.frame(rec0=sum(x$rec0[x$Era=="TIME"]))) ### <--AEN: GLOBAL ATTRIBUTES FOR CHARACTERS!!!
  zeros=which(forR0$rec0>0)
  forR0<-forR0[zeros,]

  p <- ggplot(forR0, aes(x=Year, y=rec0,colour=Model_run))
  p <- p+geom_line(stat="identity")+facet_wrap(~Area, ncol=2)+ylab('Recruit 0 (millions)')
  ggplotly(p)
  ##########################################################################
  }else{
    forR0 <- ddply(na.exclude(R0plot), .(Year,Model_run),
                 function(x) data.frame(rec0=sum(x$rec0[x$Era=="TIME"]))) ### <--AEN: GLOBAL ATTRIBUTES FOR CHARACTERS!!!
  zeros=which(forR0$rec0>0)
  forR0<-forR0[zeros,]

  p <- ggplot(forR0, aes(x=Year, y=rec0,colour=Model_run))
  p <- p+geom_line(stat="identity")+ylab('Recruit 0 (millions)')+ggtitle('single-area model')
  ggplotly(p)
  }
})
```

### Total Recruitment 
```{r}
renderPlotly({
  R0plot<-R0_plot()
  ####################### RECRUITMENT (SUMMED OVER AREAS) ###########################
  forR0 <- ddply(na.exclude(R0plot), .(Year,Model_run),
                 function(x) data.frame(rec0=sum(x$rec0[x$Era=="TIME"]))) ### <--AEN: GLOBAL ATTRIBUTES FOR CHARACTERS!!!
  zeros=which(forR0$rec0>0)
  forR0<-forR0[zeros,]

  p <- ggplot(forR0, aes(x=Year, y=rec0,colour=Model_run))
  p <- p+geom_line(stat="identity")+ylab('Recruit 0 (millions)')
  ggplotly(p)
  ##########################################################################
})
```

Selectivity
===================================== 
Size and age selectivity. Size selectivity by fleet defined as "Lsel" (cm)  in the latest year of the assessment.


Column {.tabset}
-----------------------------------------------------------------------
### Size Selectivity
```{r}
renderPlotly({
  Sselplot<-Ssel_plot()
  ####################### SIZE SELECTIVITY BY FLEET ###########################
  if(length(grep('Gender',colnames(Sselplot)))>0){ forSize <- ddply(na.exclude(Sselplot), .(Fleet,Size,Model_run),
                 function(x) data.frame(x[x$Gender==1 & x$Factor=="Lsel" & x$Year==x$endyr,]))
  }else{forSize <- ddply(na.exclude(Sselplot), .(Fleet,Size,Model_run),
                 function(x) data.frame(x[x$Factor=="Lsel" & x$Year==x$endyr,]))}
  p <- ggplot(forSize, aes(x=Size, y=sel,colour=Model_run))
p <- p+geom_line(stat="identity")+facet_wrap(~Fleet, ncol=5, scales="free")+xlab('Length (cm)')+ylab('Proportion')#+
ggplotly(p)
  ##########################################################################
})
```

### Age Selectivity
```{r}
renderPlotly({
  Aselplot<-Asel_plot()
  req(!is.null(Aselplot))
  ####################### SIZE SELECTIVITY BY FLEET ###########################
  if(length(grep('Gender',colnames(Aselplot)))>0){ forAge <- ddply(na.exclude(Aselplot), .(Fleet,Age,Model_run),
                 function(x) data.frame(x[x$Gender==1 & x$Factor=="Asel" & x$Year==x$endyr,]))
  }else{forAge <- ddply(na.exclude(Aselplot), .(Fleet,Age,Model_run),
                 function(x) data.frame(x[x$Factor=="Asel" & x$Year==x$endyr,]))}
  p <- ggplot(forAge, aes(x=Age, y=sel,colour=Model_run))
p <- p+geom_line(stat="identity")+facet_wrap(~Fleet, ncol=5, scales="free")+xlab('Length (cm)')+ylab('Proportion')#+
ggplotly(p)
  ##########################################################################
})
```
